---
title: "CheetahClock_age_sex"
output: html_notebook
---
# Data import and processing

Import data and load packages
```{r}
setwd("C:/Users/mysrael/Documents/HorvathClockR/Cheetah/Horvath_data")

# Load packages
library(glmnet)
library(ggplot2)
library(DescTools)

# Methylation data submission 1 (corrected)
beta_sesame1 <- readRDS('beta_sesame_shifted.RDS')

# Methylation data submission 2 
data_sesame2 <- readRDS('NormalizedData2/data_sesame.RDS')
beta_sesame2 <- t(data_sesame2$beta)
beta_sesame2 <- as.data.frame(beta_sesame2)

# Cheetah metadata
cheetah_info <- read.csv("cheetah_metadata_vod2.csv")

# Extract liver SIDs
liver_sids <- cheetah_info$SID[cheetah_info$Tissue == "Liver"]

# Subset methylation data: liver
beta_sesame1_liver <- beta_sesame1[rownames(beta_sesame1) %in% liver_sids, ]
beta_sesame2_liver <- beta_sesame2[rownames(beta_sesame2) %in% liver_sids, ]

# Merge to one liver df
beta_sesame_liver <- rbind(beta_sesame1_liver, beta_sesame2_liver)
```

WCGNA UH clustering for for outliers
```{r}
# Load packages
library(glmnet)
library(WGCNA)

# The following setting is important, do not omit.
options(stringsAsFactors <- FALSE);
methylation_liver <- as.data.frame(beta_sesame_liver)

datExpr00 <- methylation_liver;

# check for genes and samples with too many missing values:

datExpr00[] <- lapply(datExpr00, function(x) {
    as.numeric(as.character(x)) #make numeric
})

gsg <- goodSamplesGenes(datExpr00, verbose = 3);
gsg$allOK

# If the last statement returns TRUE, all genes have passed the cuts. If not, we remove the offending genes and samples from the data:
if (!gsg$allOK)
{
# Optionally, print the gene and sample names that were removed:
if (sum(!gsg$goodGenes)>0)
printFlush(paste("Removing genes:", paste(names(datExpr00)[!gsg$goodGenes], collapse = ", ")));
if (sum(!gsg$goodSamples)>0)
printFlush(paste("Removing samples:", paste(rownames(datExpr00)[!gsg$goodSamples], collapse = ", ")));
# Remove the offending genes and samples from the data:
datExpr00 <- datExpr00[gsg$goodSamples, gsg$goodGenes]
}

#Next we cluster the samples (in contrast to clustering genes that will come later) to see if there are any obvious outliers.
sampleTree <- hclust(dist(datExpr00), method = "average");
# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
sizeGrWindow(12,9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
abline(h = 30, col = "red"); 
```

Remove outliers (clustering + stillborns)
```{r}
# Remove by hand:
outlier_IDs <- c("ET0394TOX00092","ET0394TOX00094", "ET0394TOX00063","ET0394TOX00095", #outlier clustering
                "ET0394TOX00084","ET0394TOX00080","ET0394TOX00069") #stillborns 

beta_clock <- beta_sesame_clock[!(rownames(beta_sesame_clock) %in% outlier_IDs), ]

# subset cheetah info to only have clock samples
cheetah_info_clock <- cheetah_info[cheetah_info$SID %in% rownames(beta_clock), ]

# arrange beta clock by cheetah_info_clock order
beta_clock <- beta_clock[match(cheetah_info_clock$SID, rownames(beta_clock)), ]

save(cheetah_info_clock, file= "cheetah_info_clock.RData")
save(beta_clock, file= "beta_clock.RData")
```

Mammalian Consortium Data Browser (MCDB) methylation data import 
```{r}
# Cheetah blood MCDB data import 
mammcon_cheetah_methdata <- read.csv("cheetah_mamconsortium_betas.csv")

rownames(mammcon_cheetah_methdata) <- mammcon_cheetah_methdata$X
mammcon_cheetah_methdata <- mammcon_cheetah_methdata[,-1]
beta_sesame_mammcon <- as.data.frame(t(mammcon_cheetah_methdata))
```

SVA batch effects
```{r}
library(sva)

sva_data0 <- ComBat(t(beta_clock), batch = cheetah_info_clock$study)
sva_data <- t(sva_data0)

pca_sva <- prcomp(sva_data, scale. = FALSE)

summary(pca_sva)
plot(pca_sva)
```

## CheetahClock for age prediction

Age transformation:Needed to account for faster aging until age of sexual maturity reached
ASM = age at sexual maturity, taken from AnAge
Functions based on log-linear age for Clock 3 in universal DNA methylation age paper
```{r}
ASM <- 2
age_transformed <- Vectorize(function(x, maturity=ASM) {
  if (is.na(x) | is.na(maturity)) {return(NA)}
  k <- 0.2
  y <- 0
  if (x < maturity) {y = log((x+k)/(maturity+k))}
  else {y = (x-maturity)/(maturity+k)}
  return(y)
})
```

Inverse transformation 
```{r}
age_inv_transformed <- Vectorize(function(y, maturity=ASM) {
  if (is.na(y) | is.na(maturity)) {return(NA)}
  k <- 0.2
  x <- 0
  if (y < 0) {x = (maturity+k)*exp(y)-k}
  else {x = (maturity+k)*y+maturity}
  return(x)
})
```

Make df with transformed ages
```{r}
age_trans = age_transformed(cheetah_info_clock$Age_yr,ASM)

# DF with ID, age, age_trans + other metadata
info_clock <- data.frame(cheetah_info_clock$SID,cheetah_info_clock$sex,cheetah_info_clock$Age_yr,age_trans)

# change col names 
colnames(info_clock) = c("SID","sex", "Age", "age_trans")
```

Elastic Net Regression with LOOCV
```{r}
# Variables
alpha <- 0.5
n <- length(age_trans) #number of samples

EN_methylation_data <- t(sva_data)

EN_age <- info_clock$age_trans

# generate a lambda value using the "cv.glmnet()" function
glmnet_cv_training <- cv.glmnet(EN_methylation_data, EN_age, alpha = alpha, family="gaussian", nfolds = n)

# Display the optimal lambda
best_lambda <- glmnet_cv_training$lambda.min
cat("Optimal Lambda:", best_lambda, "\n")

# LOOCV
model_list <- list() # empty list to take in model iterations
for (i in 1:nrow(info_clock)){
  meth_data_loo <- EN_methylation_data[-i,]
  age_data_loo <-EN_age[-i]
  test_id <- as.matrix(EN_methylation_data[i,])
  test_id <-t(test_id)
  
  fit <- glmnet(x=meth_data_loo, y=age_data_loo,lambda = best_lambda,alpha=alpha,family="gaussian")
  model_list[[i]] <- fit #store model in list
}

# Calculate MSE for each model
mse_values <- sapply(model_list, function(model) {
  predictions <- predict(model, newx = EN_methylation_data, type = "response")
  mean((predictions - EN_age)^2)
})

# Identify the index of the model with the minimum MSE
best_model_index <- which.min(mse_values)

# Access the best model
best_model1 <- model_list[[best_model_index]]

# Get age predictions using best_model
y.best_model1 <- predict(best_model1,EN_methylation_data, type = "response")
info_clock$DNAmoClockLOO <- y.best_model1

# Save model
saveRDS(best_model1, "CheetahClock_age.rds")
```

Check output
```{r}
# Inverse age function on output
age_inv_trans <- age_inv_transformed(info_clock$DNAmoClockLOO,ASM)
info_clock$age_inv_trans <- age_inv_trans

# error LOOCV
errorLOOCV <- info_clock$Age - info_clock$age_inv_trans
MAE_LOOCV <- sqrt(median(errorLOOCV^2))
MAE_LOOCV

# pearson correlation LOOCV
r_LOOCV <- cor(info_clock$Age, info_clock$age_inv_trans, method = "pearson")
r_LOOCV

#plot LOOCV
Plot <- ggplot(info_clock, aes(x = Age, y = age_inv_trans)) +
  ylim(0,20) + xlim(0,20) +
  geom_point(shape=1, size=2) +
  geom_smooth(method = "lm", se = FALSE, fullrange = TRUE, colour="deepskyblue4") +
  geom_abline(intercept = 0, slope = 1, linetype = 3)+
  theme_classic()+
  theme(axis.title=element_blank(), axis.text = element_text(size=14, colour = "black"),);Plot
```

Inspect best_clock coefs
```{r}
#Inspect model coefficients (beta vals):
coefs <- as.matrix(coef(best_model1, s = best_lambda))
chosen_features <- rownames(coefs)[coefs !=0]
print(coefs[chosen_features, , drop=FALSE])
number_chosen_features <- length(chosen_features)
cat("number of chosen CpG sites:", number_chosen_features, "\n")

#save features
cheetahclock_age_coefs <- chosen_features
save(cheetahclock_age_coefs, file = "CheetahClock_age_coefs.Rdata")

cpgs_coefs <- (coefs[chosen_features, , drop=FALSE])
as.data.frame(cpgs_coefs)
write.csv(cpgs_coefs, file = "CheetahClock_age_cpgs.csv", row.names = TRUE)
```

Assess clock
```{r}
# Plot age vs DNAm age
a<-info_clock$Age
b<-info_clock$age_inv_trans
cor0<-round(cor(a,b),2)
mae0<-round(median(abs(a-b)),2)
plot(a,b,xlab='Age',ylab='DNAm age',
     main=paste0('CheetahClock LOO Liver and Blood (n=',length(a),')\n','cor=',cor0,
                 ', MAE=',mae0),
     col='white',xlim=c(-1,max(max(a),max(b))+1),
     ylim=c(-1,max(max(a),max(b))+1),
     cex.lab = 1.25) #axis label size

# Color ID labels
ID = info_clock$SID
label_colors = rep("blue", length(ID))

# Color code by study
ID_mammcon <- cheetah_info_clock$SID[cheetah_info_clock$study == "MammCon"]
ID_sdzwa <- cheetah_info_clock$SID[cheetah_info_clock$study == "SDZWA"]

mammcon_color = "sienna1"
sdzwa_color = "green4"

for (i in 1:length(ID)) {
  if (ID[i] %in% ID_mammcon) {
    label_colors[i] <- mammcon_color
  } else if (ID[i] %in% ID_sdzwa) {
    label_colors[i] <- sdzwa_color
  }
  points(a[i], b[i], col = label_colors[i], pch=16)
}

legend_labels <- c("MCDB blood","SDZWA liver")
legend_colors <- c("sienna1","green4")
legend("bottomright", legend = legend_labels, fill = legend_colors)

abline(0,1,lwd=2,lty=2,col="grey")
model1 <- lm(b~a)
abline(model1,lwd=2,lty=2,col='black')
```

## CheetahClock age validation (submission 2 data)

# SDZWA blood samples
```{r}
# Extract blood SIDs
blood_sids <- cheetah_info$SID[cheetah_info$Tissue == "Blood" & cheetah_info$submission == 2]

# Subset methylation data so only blood
beta_test_blood <- beta_sesame2[rownames(beta_sesame2) %in% blood_sids, ]

# subset cheetah info to only have blood samples
cheetah_info_blood <- cheetah_info[cheetah_info$SID %in% rownames(beta_test_blood), ]

# arrange by cheetah_info_blood order
beta_test_blood <- beta_test_blood[match(cheetah_info_blood$SID, rownames(beta_test_blood)), ]
```

Quick check with WCGNA
```{r}
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE);
methylation_blood <- as.data.frame(beta_test_blood)

datExpr00 <- methylation_blood;

# check for genes and samples with too many missing values:
datExpr00[] <- lapply(datExpr00, function(x) {
    as.numeric(as.character(x)) #make numeric
})

gsg <- goodSamplesGenes(datExpr00, verbose = 3);
gsg$allOK

# If the last statement returns TRUE, all genes have passed the cuts. If not, we remove the offending genes and samples from the data:
if (!gsg$allOK)
{
# Optionally, print the gene and sample names that were removed:
if (sum(!gsg$goodGenes)>0)
printFlush(paste("Removing genes:", paste(names(datExpr00)[!gsg$goodGenes], collapse = ", ")));
if (sum(!gsg$goodSamples)>0)
printFlush(paste("Removing samples:", paste(rownames(datExpr00)[!gsg$goodSamples], collapse = ", ")));
# Remove the offending genes and samples from the data:
datExpr00 <- datExpr00[gsg$goodSamples, gsg$goodGenes]
}

#Next we cluster the samples (in contrast to clustering genes that will come later) to see if there are any obvious outliers.
sampleTree <- hclust(dist(datExpr00), method = "average");
# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
sizeGrWindow(12,9)
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Blood Sample Clustering", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
```

Make blood info DF
```{r}
# subset cheetah info to only have blood samples
cheetah_info_blood <- cheetah_info[cheetah_info$SID %in% rownames(beta_test_blood), ]

# arrange by cheetah_info_blood order
beta_test_blood <- beta_test_blood[match(cheetah_info_blood$SID, rownames(beta_test_blood)), ]
```

Test on blood
```{r}
# Run model on new data
EN_test_blood <- as.matrix(beta_test_blood)
y.blood <- predict(best_model1,EN_test_blood, type = "response")

# Inverse age function on output
y.blood_age_inv <- age_inv_transformed(y.blood,ASM)

# Output DF
output_blood <- data.frame(cheetah_info_blood$SID,cheetah_info_blood$Age_yr,y.blood,y.blood_age_inv)
colnames(output_blood) <- c("SID", "Age", "s0", "Age_inv")

# Plot age vs DNAm age
a <- output_blood$Age
b <- output_blood$Age_inv
cor0 <- round(cor(a,b),2)
mae0 <- round(median(abs(a-b)),2)
plot(a,b,xlab='Age',ylab='DNAm age',
     main=paste0('CheetahClock Test Blood (n=',length(a),')\n','cor=',cor0,
                 ', MAE=',mae0),
     col='darkgreen',xlim=c(-1,max(max(a),max(b))+1),
     ylim=c(-1,max(max(a),max(b))+1),
     cex.lab = 1.25) #axis label size

points(a, b, col = 'darkgreen', pch=16, cex=1.25)
abline(0,1,lwd=2,lty=2,col="grey")
model1<-lm(b~a)
abline(model1,lwd=,lty=2,col='black')
```

# SDZWA skin
```{r}
# Extract skin SIDs
skin_sids <- cheetah_info$SID[cheetah_info$Tissue == "Skin"]

# Subset methylation data so only skin
beta1_test_skin <- beta_sesame1[rownames(beta_sesame1) %in% skin_sids, ]
beta2_test_skin <- beta_sesame2[rownames(beta_sesame2) %in% skin_sids, ]
beta_test_skin <- rbind(beta1_test_skin,beta2_test_skin)

# subset cheetah info to only have skin samples
cheetah_info_skin <- cheetah_info[cheetah_info$SID %in% rownames(beta_test_skin), ]

# arrange by cheetah_info_skin order
beta_test_skin <- beta_test_skin[match(cheetah_info_skin$SID, rownames(beta_test_skin)), ]
```

Quick check with WCGNA
```{r}
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE);
methylation_skin <- as.data.frame(beta_test_skin)

datExpr00 <- methylation_skin;

# check for genes and samples with too many missing values:
datExpr00[] <- lapply(datExpr00, function(x) {
    as.numeric(as.character(x)) #make numeric
})

gsg <- goodSamplesGenes(datExpr00, verbose = 3);
gsg$allOK

# If the last statement returns TRUE, all genes have passed the cuts. If not, we remove the offending genes and samples from the data:
if (!gsg$allOK)
{
# Optionally, print the gene and sample names that were removed:
if (sum(!gsg$goodGenes)>0)
printFlush(paste("Removing genes:", paste(names(datExpr00)[!gsg$goodGenes], collapse = ", ")));
if (sum(!gsg$goodSamples)>0)
printFlush(paste("Removing samples:", paste(rownames(datExpr00)[!gsg$goodSamples], collapse = ", ")));
# Remove the offending genes and samples from the data:
datExpr00 <- datExpr00[gsg$goodSamples, gsg$goodGenes]
}

#Next we cluster the samples (in contrast to clustering genes that will come later) to see if there are any obvious outliers.
sampleTree <- hclust(dist(datExpr00), method = "average");
# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
sizeGrWindow(12,9)
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Skin Sample Clustering", sub="", xlab="", cex.lab = 1.5,
cex.axis = 1.5, cex.main = 2)
abline(h = 15, col = "red");
```

Outlier removal
```{r}
# Remove by hand:
outlier_IDs_skin <- c("ET0560TOX00458") #outlier clustering

beta_test_skin <- beta_test_skin[!(rownames(beta_test_skin) %in% outlier_IDs_skin), ]

# subset cheetah info to only have skin samples
cheetah_info_skin <- cheetah_info[cheetah_info$SID %in% rownames(beta_test_skin), ]

# arrange by cheetah_info_skin order
beta_test_skin <- beta_test_skin[match(cheetah_info_skin$SID, rownames(beta_test_skin)), ]
```

Test on skin
```{r}
# Run model on new data
EN_test_skin <- as.matrix(beta_test_skin)
y.skin <- predict(best_model1,EN_test_skin, type = "response")

# Inverse age function on output
y.skin_age_inv <- age_inv_transformed(y.skin,ASM)

# Output DF
output_skin <- data.frame(cheetah_info_skin$SID,cheetah_info_skin$Age_yr,y.skin,y.skin_age_inv)
colnames(output_skin) <- c("SID", "Age", "s0", "Age_inv")

# Plot age vs DNAm age
a <- output_skin$Age
b <- output_skin$Age_inv
cor0 <- round(cor(a,b),2)
mae0 <- round(median(abs(a-b)),2)
plot(a,b,xlab='Age',ylab='DNAm age',
     main=paste0('CheetahClock Test Skin (n=',length(a),')\n','cor=',cor0,
                 ', MAE=',mae0),
     col='green4',xlim=c(-1,max(max(a),max(b))+1),
     ylim=c(-1,max(max(a),max(b))+1),
     cex.lab = 1.25) #axis label size
points(a, b, col = 'green4', pch=16, cex=1.25)
abline(0,1,lwd=2,lty=2,col="grey")
model1=lm(b~a)
abline(model1,lwd=2,lty=2,col='black')

legend_labels <- c("SDZWA skin")
legend_colors <- c("darkgreen")
legend("bottomright", legend = legend_labels, fill = legend_colors)
```

Variance calculations
```{r}
# Sample data frame
df_var_LOOCV <- data.frame(
  SID = info_clock$SID,
    predicted_age = info_clock$age_inv_trans,
    actual_age = info_clock$Age
)

df_var_LOOCV$difference <- abs(df_var_LOOCV$predicted_age - df_var_LOOCV$actual_age)

df_var_LOOCV$percent_variation <- (df_var_LOOCV$difference / df_var_LOOCV$actual_age) * 100

print(df_var_LOOCV)
write.csv(df_var_LOOCV, file = "CheetahClock_LOOCV_results.csv", row.names = TRUE)

# Blood
df_var_blood <- data.frame(
  SID = output_blood$SID,
    predicted_age = output_blood$Age_inv,
    actual_age = output_blood$Age
)

df_var_blood$difference <- abs(df_var_blood$predicted_age - df_var_blood$actual_age)

df_var_blood$percent_variation <- (df_var_blood$difference / df_var_blood$actual_age) * 100

print(df_var_blood)
write.csv(df_var_blood, file = "CheetahClock_blood_results.csv", row.names = TRUE)

# Skin
df_var_skin <- data.frame(
  SID = output_skin$SID,
    predicted_age = output_skin$Age_inv,
    actual_age = output_skin$Age
)

df_var_skin$difference <- abs(df_var_skin$predicted_age - df_var_skin$actual_age)

df_var_skin$percent_variation <- (df_var_skin$difference / df_var_skin$actual_age) * 100

print(df_var_skin)
write.csv(df_var_skin, file = "CheetahClock_skin_results.csv", row.names = TRUE)
```


## CheetahClock for sex prediction
```{r}
# Remove NA:
NA_IDs = c("X204529320040_R04C02") # MCDB sample w sex=NA 	

beta_sex <- beta_clock[!(rownames(beta_clock) %in% NA_IDs), ]

# subset cheetah info to only have clock samples
cheetah_info_sex <- cheetah_info[cheetah_info$SID %in% rownames(beta_sex), ]

# arrange beta clock by cheetah_info_clock order
beta_sex <- beta_sex[match(cheetah_info_sex$SID, rownames(beta_sex)), ]
```

Make binomial gmlnet with CV to find best lambda
```{r}
# Variables
alpha <- 0.5
n <- length(cheetah_info_sex$sex) #number of samples
EN_methylation_data <- as.matrix(beta_sex)
EN_sex <- cheetah_info_sex$sex

# generate a lambda value using the "cv.glmnet()" function
glmnet_cv_training_sex <- cv.glmnet(EN_methylation_data, EN_sex, alpha = alpha, family="binomial", nfolds = n)

# Display the optimal lambda
best_lambda_sex <- glmnet_cv_training_sex$lambda.min

# Fit the best model using glmnet with the best lambda
best_model_sex <- glmnet(EN_methylation_data, EN_sex, alpha = alpha, family = "binomial", lambda = best_lambda_sex)

# Save model
saveRDS(best_model_sex, "CheetahClock_sex.rds")

# To make predictions on the same dataset
predicted_prob <- predict(best_model_sex, EN_methylation_data, type = "response")

# Convert probabilities to binary classification: "M" for Male, "F" for Female
predicted_sex <- ifelse(predicted_prob >= 0.5, "M", "F")

# add the predictions to DF
cheetah_info_sex$predicted_sex <- as.vector(predicted_sex)
```

Inspect best_clock coefs
```{r}
#Inspect model coefficients (beta vals):
coefs_sex <- as.matrix(coef(best_model_sex, s = best_lambda_sex))
chosen_features_sex <- rownames(coefs_sex)[coefs_sex !=0]
print(coefs_sex[chosen_features_sex, , drop=FALSE])
number_chosen_features_sex <- length(chosen_features_sex)
cat("number of chosen CpG sites:", number_chosen_features_sex, "\n")

#save features
cheetahclock_sex_coefs <- chosen_features_sex
save(cheetahclock_sex_coefs, file <- "cheetahclock_sex_coefs.Rdata")

sex_cpgs_coefs <- (coefs_sex[cheetahclock_sex_coefs, , drop=FALSE])
as.data.frame(sex_cpgs_coefs)
write.csv(sex_cpgs_coefs, file = "cheetahclock_sex_cpgs_coefs.csv", row.names = TRUE)
```

## CheetahClock sex validation (submission 2 data)
```{r}
# Extract skin SIDs
submission2_sids <- cheetah_info$SID[cheetah_info$submission == "2"]

# Subset methylation data so only skin
beta_test_sex <- beta_sesame2[rownames(beta_sesame2) %in% submission2_sids, ]

# subset cheetah info to only have submission2 samples
cheetah_info_sex_test <- cheetah_info[cheetah_info$SID %in% rownames(beta_test_sex), ]

# arrange by cheetah_info_sex_test
cheetah_info_sex_test <- cheetah_info_sex_test[match(cheetah_info_sex_test$SID, rownames(beta_test_sex)), ]

# Run model on new data
EN_test_sex <- as.matrix(beta_test_sex)
predicted_prob <- predict(best_model_sex,EN_test_sex, type = "response")

# Convert probabilities to binary classification: "M" for Male, "F" for Female
predicted_sex <- ifelse(predicted_prob >= 0.5, "M", "F")

# Output DF
output_sex <- data.frame(cheetah_info_sex_test$SID,cheetah_info_sex_test$sex,predicted_sex)
colnames(output_sex) <- c("SID", "sex", "predicted_sex")

# Calculate proportion agreement
proportion_agreement <- sum(output_sex$sex == output_sex$predicted_sex) / nrow(output_sex)
print(paste("Proportion Agreement:", proportion_agreement))

# Find rows where the predicted sex does not match the actual sex
disagreement_rows <- subset(output_sex, predicted_sex != sex)

# Print the rows with disagreement
disagreement_IDs <- disagreement_rows$SID
cat("IDs with Disagreement:", disagreement_IDs, "\n")
```